\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=purple,urlcolor=blue]{hyperref}
\usepackage[capitalise,nameinlink]{cleveref}
\usepackage{cite}

%% ============================================================
%% Theorem Environments
%% ============================================================
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{openproblem}[theorem]{Open Problem}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{notation}[theorem]{Notation}
\newtheorem*{erratum}{Erratum}

%% ============================================================
%% Custom Commands
%% ============================================================
\newcommand{\Hilbert}{\mathcal{H}}
\newcommand{\Fock}{\mathcal{F}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\half}{\tfrac{1}{2}}
\newcommand{\qint}[1]{[#1]_q}             % quantum integer
\newcommand{\qfact}[1]{[#1]_q!}           % quantum factorial
\newcommand{\qdim}[1]{d_{#1}}             % quantum dimension
\newcommand{\sixj}[6]{\begin{Bmatrix} #1 & #2 & #3 \\ #4 & #5 & #6 \end{Bmatrix}}
\newcommand{\threej}[6]{\begin{pmatrix} #1 & #2 & #3 \\ #4 & #5 & #6 \end{pmatrix}}
\newcommand{\TV}{\ensuremath{\mathrm{TV}}}
\newcommand{\PR}{\ensuremath{\mathrm{PR}}}
\newcommand{\CS}{\ensuremath{\mathrm{CS}}}
\newcommand{\GFT}{\ensuremath{\mathrm{GFT}}}
\newcommand{\BLM}{\ensuremath{\mathrm{BLM}}}
\newcommand{\SYK}{\ensuremath{\mathrm{SYK}}}
\newcommand{\SD}{\ensuremath{\mathrm{SD}}}
\newcommand{\BPS}{\ensuremath{\mathrm{BPS}}}
\newcommand{\Vol}{\ensuremath{\mathrm{Vol}}}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Pf}{Pf}
\DeclareMathOperator{\kernel}{ker}

%% AF node cross-reference command
%% Usage: \afnode{1.3.2} produces a margin note + hyperlink
\newcommand{\afnode}[1]{\marginpar{\tiny\textsf{AF:#1}}\label{af:#1}}
\newcommand{\afref}[1]{(AF node~#1, p.~\pageref{af:#1})}

%% Epistemic status markers
\newcommand{\established}{\textsf{\small [ESTABLISHED]}}
\newcommand{\conjectural}{\textsf{\small [CONJECTURAL]}}
\newcommand{\mixedstatus}{\textsf{\small [MIXED STATUS]}}
\newcommand{\openstatus}{\textsf{\small [OPEN]}}

%% ============================================================
%% Title
%% ============================================================
\title{\textbf{The $q$-Deformed BLM Model:\\Quantum Groups, SUSY, and 3D Gravity}\\[0.5em]
\large A Self-Contained Account with Adversarial Verification}
\author{Generated from AF Proof Tree v2}
\date{\today}

%% ============================================================
%% Document
%% ============================================================
\begin{document}

\maketitle

\begin{abstract}
We present a comprehensive account of the $q$-deformed BLM (Biggs--Lin--Maldacena) model,
a supersymmetric quantum mechanical system whose supercharge is constructed from
quantum $3j$ symbols of $U_q(\mathfrak{su}(2))$.
The model exhibits three geometric regimes of decreasing epistemic certainty:
(I)~the Euclidean regime at $q=1$, where melonic dominance yields SYK-type solvability
with Ponzano--Regge (flat 3D gravity) asymptotics;
(II)~the hyperbolic regime at fixed real $q \neq 1$, where exponential growth of
quantum recoupling symbols is \emph{conjectured} to break melonic dominance;
(III)~the root-of-unity regime $q = e^{2\pi i/r}$, where the model connects to
Turaev--Viro topological invariants and 3D gravity with positive cosmological constant.
All claims have been subjected to adversarial prover--verifier review, with each
result traced to its corresponding node in the proof tree.
This paper is self-contained and assumes only a graduate-level physics background.
\end{abstract}

\setcounter{tocdepth}{2}
\tableofcontents
\newpage

%% ============================================================
%% Sections (each in a separate file)
%% ============================================================

\input{sections/01_introduction}

\input{sections/02_model_definition}

\input{sections/03_part1_euclidean}

\input{sections/04_part2_hyperbolic}

\input{sections/05_part3_root_of_unity}

\input{sections/06_open_problems}

\input{sections/07_conclusion}

\input{sections/appendix_af_tree}

%% ============================================================
%% Bibliography
%% ============================================================
\begin{thebibliography}{99}

\bibitem{BLM} A.~Biggs, L.~L.~Lin, and J.~Maldacena,
``A melonic quantum mechanical model without disorder,''
arXiv:2601.08908 [hep-th] (2026).

\bibitem{SYK-Fu} W.~Fu, D.~Gaiotto, J.~Maldacena, and S.~Sachdev,
``Supersymmetric Sachdev-Ye-Kitaev models,''
Phys.\ Rev.\ D \textbf{95}, 026009 (2017), arXiv:1610.08917.

\bibitem{TV92} V.~G.~Turaev and O.~Ya.~Viro,
``State sum invariants of 3-manifolds and quantum 6j-symbols,''
Topology \textbf{31}, 865--902 (1992).

\bibitem{TuraevWalker} V.~G.~Turaev,
``Quantum invariants of knots and 3-manifolds,''
de Gruyter Studies in Mathematics \textbf{18} (1994).

\bibitem{PonzanoRegge} G.~Ponzano and T.~Regge,
``Semiclassical limit of Racah coefficients,''
in \emph{Spectroscopic and Group Theoretical Methods in Physics},
ed.~F.~Bloch et al., North-Holland (1968).

\bibitem{Boulatov} D.~V.~Boulatov,
``A model of three-dimensional lattice gravity,''
Mod.\ Phys.\ Lett.\ A \textbf{7}, 1629 (1992).

\bibitem{Freidel} L.~Freidel,
``Group field theory: An overview,''
Int.\ J.\ Theor.\ Phys.\ \textbf{44}, 1769 (2005), arXiv:hep-th/0505016.

\bibitem{BellettiYang} S.~Belletti and T.~Yang,
``Asymptotics of quantum 6j symbols,''
J.\ Topology \textbf{18} (2025), arXiv:2308.13864.

\bibitem{Costantino} F.~Costantino,
``6j-symbols, hyperbolic structures and the volume conjecture,''
Geom.\ Topol.\ \textbf{11}, 1831--1854 (2007).

\bibitem{TaylorWoodward} Y.~U.~Taylor and C.~T.~Woodward,
``6j symbols for $U_q(\mathfrak{sl}_2)$ and non-Euclidean tetrahedra,''
Selecta Math.\ (N.S.) \textbf{11}, 539--571 (2005).

\bibitem{Kashaev} R.~M.~Kashaev,
``The hyperbolic volume of knots from the quantum dilogarithm,''
Lett.\ Math.\ Phys.\ \textbf{39}, 269--275 (1997).

\bibitem{MurakamiMurakami} H.~Murakami and J.~Murakami,
``The colored Jones polynomials and the simplicial volume of a knot,''
Acta Math.\ \textbf{186}, 85--104 (2001).

\bibitem{MizoguchiTada} S.~Mizoguchi and T.~Tada,
``Three-dimensional gravity from the Turaev-Viro invariant,''
Phys.\ Rev.\ Lett.\ \textbf{68}, 1795 (1992).

\bibitem{BenGelounBonzom} J.~Ben Geloun and V.~Bonzom,
``Radiative corrections in the Boulatov-Ooguri tensor model,''
Nucl.\ Phys.\ B \textbf{867}, 399 (2013), arXiv:1101.4294.

\bibitem{BenGelounRivasseau} J.~Ben Geloun and V.~Rivasseau,
``A renormalizable SYK-type tensor field theory,''
Ann.\ Henri Poincar\'e \textbf{19}, 3357 (2018), arXiv:1711.05967.

\bibitem{Faddeev} L.~D.~Faddeev,
``Modular double of quantum group,''
Math.\ Phys.\ Stud.\ \textbf{21}, 149--156 (2000), arXiv:math/9912078.

\bibitem{PonsotTeschner} B.~Ponsot and J.~Teschner,
``Liouville bootstrap via harmonic analysis on a noncompact quantum group,''
arXiv:hep-th/9911110 (1999).

\bibitem{TeschnerVartanov} J.~Teschner and G.~S.~Vartanov,
``Supersymmetric gauge theories, quantization of $\mathcal{M}_\mathrm{flat}$,
and conformal field theory,''
Adv.\ Theor.\ Math.\ Phys.\ \textbf{19}, 1--135 (2015), arXiv:1302.3572.

\bibitem{BDKY} S.~Belletti, R.~Detcherry, E.~Kalfagianni, and T.~Yang,
``Growth of quantum 6j-symbols and applications to the Volume Conjecture,''
J.\ Diff.\ Geom.\ \textbf{120}, 199--248 (2022).

\end{thebibliography}

\end{document}
